---
title: "question 1 readme"
author: "Gabriel Rambanapasi"
date: "`r Sys.Date()`"
output: html_document
---

# question 1 

```{r}
# loadings 
library(pacman, gt)
p_load("tidyverse")

ASISA <- read_rds("data/ASISA_Rets.rds")
BM <- read_rds("data/Capped_SWIX.rds") 
AI <- read_rds("data/AI_Max_Fund.rds")

# clean up the data to merge the datasets, its already monthly data
ASISA <- ASISA %>% select(date, Fund, Returns)
AI <- AI %>% mutate(`Fund` = " AI") %>% rename(Returns = `AI_Fund`) %>%  select(date, Fund, Returns )
BM <- BM %>% rename( Fund = "Tickers")
```

# objective 


- im going to show after the fee performance for an actively managed fund and AI fund compares to that of the benchmark.  

- i will use excess returns to depict the difference in performnace 

- for fund performance, I will use  information ratios, this is my best measure to compare risk adjusted performance. 

- im going to assume a standard indusrty fee of 1.5% for active managers and the AI fund.

```{r}
# starting with comparables for the benchmarks ASISA and SWIX 

# lets find out when these indexes started and look for the best, worst and median performing funds 

# Funds that have the greatest vintage 
Funds_inception_in_2003 <- ASISA %>%
  arrange(date) %>%
  group_by(Fund) %>%
  mutate(Y = format(date,"%Y")) %>% filter(Y %in% 2003) %>% select(Fund) %>% distinct() %>% pull()

#  sanity check

# ASISA %>%
#   filter(Fund %in% Funds_inception_in_2003$Fund) %>%
#   mutate(YM = format(date, "%Y-%m")) %>%
#   group_by(Fund) %>%
#   summarise(HasRecordsFor2023 = all(2023 %in% year(date))) %>%
#   filter(HasRecordsFor2023) %>%
#   select(Fund)


top_funds_comparison_to_the_benchmark <- ASISA %>%
  arrange(date) %>%
  group_by(Fund) %>%
  filter(Fund %in%Funds_inception_in_2003) %>%
  select(date, Fund, Returns) %>%
    mutate(YM = format(date, "%y %b")) %>% 
  summarise(Inception = first(date), Cumulative_Return = prod(1 + Returns)) %>%
  arrange(desc(Cumulative_Return)) %>%
  slice_head(n = 5) %>% bind_rows(BM %>% filter(date >= lubridate::ymd(20031031)) %>% summarise(Fund = "SWIX",Inception = first(date),  Cumulative_Return = prod(1 + Returns)))# this is before fees 


# top_funds_comparison_to_the_benchmark
# 
# table1 <- gt(top_funds_comparison_to_the_benchmark)

gtsave(table1 , file = "output_table.html")

# now i want get net of fee returns 

top_funds<- ASISA %>%
  arrange(date) %>%
  group_by(Fund) %>%
  filter(Fund %in%Funds_inception_in_2003) %>%
  select(date, Fund, Returns) %>%
    mutate(YM = format(date, "%y %b")) %>% 
  summarise(Inception = first(date), Cumulative_Return = prod(1 + Returns)) %>%
  arrange(desc(Cumulative_Return)) %>%
 slice_head(n = 5) %>% select(Fund) %>% distinct %>% pull()

Net_of_top_managers  <- ASISA %>% 
    filter (Fund %in% top_funds) %>% 
    mutate(YM = format(date, "%y %b")) %>%
    group_by(YM) %>% 
    filter(date == last(date)) %>% ungroup() %>% select(-YM ) %>% 
    mutate(fee_calc(., 150)) %>% 
    group_by(Fund) %>% 
    summarise(Inception = first(date), Cumulative_Return = prod(1 + `Net of fees`) - 1) %>%
  arrange(desc(Cumulative_Return)) %>% 
    bind_rows(BM %>% filter(date >= lubridate::ymd(20031031)) %>% summarise(Fund = "SWIX",  Inception = first(date), Cumulative_Return = prod(1 + Returns))) # after fees 

Net_of_top_managers

 table2 <- gt(Net_of_top_managers)
 
 gtsave(table2 , file = "output_table2.html")

```


```{r}
# now for the distributional arguments

# top manager

Monthly_returns <- ASISA %>% 
    filter (Fund %in% top_funds) %>% 
    mutate(YM = format(date, "%y %b")) %>%
    group_by(YM) %>% 
    filter(date == last(date)) %>%
    ungroup() %>% select(-YM )

BM <- BM %>% filter(date >= lubridate::ymd(20031031))

combined_return <- bind_rows(BM, Monthly_returns) %>% group_by(Fund) 

topmanager <- combined_return %>%
  ggplot(aes(x = Fund, y = Returns, color = Fund)) +
  geom_violin() +
  geom_jitter(width = 0.15, alpha = 0.8) +
  scale_y_continuous(labels = scales::percent) +
  theme_minimal() +
  labs(title = "Distribution of Returns",
       subtitle = "Performance of good funds is similar to benchmark",  # Add the subtitle here
       x = "", y = "Return") +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", size = 13),
        plot.title.position = "plot")

 ggsave("topmanager.jpg", topmanager, width = 6, height = 4, units = "in", dpi = 300)

```


```{r}

 # bottom managers
bottom_funds_comparison_to_the_benchmark <- ASISA %>%
  arrange(date) %>%
  group_by(Fund) %>%
  filter(Fund %in%Funds_inception_in_2003) %>%
  select(date, Fund, Returns) %>%
    mutate(YM = format(date, "%y %b")) %>% 
  summarise(Inception = first(date), Cumulative_Return = prod(1 + Returns)) %>%
  arrange((Cumulative_Return)) %>%
  slice_head(n = 5) %>% bind_rows(BM %>% filter(date >= lubridate::ymd(20031031)) %>% summarise(Fund = "SWIX",Inception = first(date),  Cumulative_Return = prod(1 + Returns)))# this is before fees 

bottom_funds_comparison_to_the_benchmark

 table3 <- gt(bottom_funds_comparison_to_the_benchmark)

  gtsave(table3 , file = "output_table3.html")

bottom_funds<- ASISA %>%
  arrange(date) %>%
  group_by(Fund) %>%
  filter(Fund %in%Funds_inception_in_2003) %>%
  select(date, Fund, Returns) %>%
    mutate(YM = format(date, "%y %b")) %>% 
  summarise(Inception = first(date), Cumulative_Return = prod(1 + Returns)) %>%
  arrange((Cumulative_Return)) %>%
  slice_head(n = 5) %>% select(Fund) %>% distinct %>% pull()

Net_of_bottom_managers  <- ASISA %>% 
    filter (Fund %in% bottom_funds) %>% 
    mutate(YM = format(date, "%y %b")) %>%
    group_by(YM) %>% 
    filter(date == last(date)) %>% ungroup() %>% select(-YM ) %>% 
    mutate(fee_calc(., 150)) %>% 
    group_by(Fund) %>% 
    summarise(Inception = first(date), Cumulative_Return = prod(1 + `Net of fees`) - 1) %>%
  arrange(desc(Cumulative_Return)) %>% 
    bind_rows(BM %>% filter(date >= lubridate::ymd(20031031)) %>% summarise(Fund = "SWIX",  Inception = first(date), Cumulative_Return = prod(1 + Returns))) # after fees 

 table4 <- gt(bottom_funds_comparison_to_the_benchmark)
 
 gtsave(table4 , file = "output_table4.html")
```

```{r}
# bad manager perfomance
Monthly_returns <- ASISA %>% 
    filter (Fund %in% bottom_funds) %>% 
    mutate(YM = format(date, "%y %b")) %>%
    group_by(YM) %>% 
    filter(date == last(date)) %>%
    ungroup() %>% select(-YM )

BM <- BM %>% filter(date >= lubridate::ymd(20031031))

combined_return <- bind_rows(BM, Monthly_returns) %>% group_by(Fund) 

bottommanager <- combined_return %>%
  ggplot(aes(x = Fund, y = Returns, color = Fund)) +
  geom_violin() +
  geom_jitter(width = 0.15, alpha = 0.8) +
  scale_y_continuous(labels = scales::percent) +
  theme_minimal() +
  labs(title = "Distribution of Returns",
       subtitle = "Performance of bad funds has questionable returns, hard to determine manager skill",  
       x = "", y = "Return") +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", size = 13),
        plot.title.position = "plot")
 
 ggsave("bottommanger.jpg", bottommanager, width = 6, height = 4, units = "in", dpi = 300)
```

