---
title: "question 1 readme"
author: "Gabriel Rambanapasi"
date: "`r Sys.Date()`"
output: html_document
---

# question 1 

```{r}
ASISA <- read_rds("data/ASISA_Rets.rds")
BM <- read_rds("data/Capped_SWIX.rds") 
AI <- read_rds("data/AI_Max_Fund.rds")

# clean up the data to merge the datasets, its already monthly data
ASISA <- ASISA %>% select(date, Fund, Returns)
AI <- AI %>% mutate(`Fund` = " AI") %>% rename(Returns = `AI_Fund`) %>%  select(date, Fund, Returns )
BM <- BM %>% rename( Fund = "Tickers")
```

- im going to show after fee performance for an actively managed fund, AI fund comapres to that of the benchmark, the metric of choice here will be the excess returns.
- going to focus on risk adjusted return using information ratios, to comapre between the active manager and AI fund. 
- im going to assume a standard indusrty fee of 1.5% for active managers and the AI fund.

```{r}

# we have gross returns, lets subtract fees to get net of fee returns 

# create a function, that calculates returns net of fees

fee_calc <- function(df, fee) {
  
  # annualize the rate 
  feeconverter <- function(fee) { 
    fee_monthly = (1 + fee / 10000)^(1 / 12) - 1
    fee_monthly
  }
  
  df <- df %>% 
    mutate(`Net of fees` = Returns - feeconverter(fee))  # Corrected the feeconverter argument
  
  return(df)  # Explicitly return the modified dataframe
}

topfunds <- ASISA %>% 
  group_by(Fund) %>% 
  summarize(`average return` = mean(Returns)) %>% 
  arrange(desc(`average return`)) %>% 
  filter(rank(desc(`average return`)) <= 10) %>% pull(Fund)

# make asisa an equally weight active fund. they comapre with your own AI fund. 

fund_comp <- bind_rows(
  BM,
  AI %>% fee_calc(150),
  ASISA %>% fee_calc(150) %>% filter(Fund %in% topfunds)
) %>%arrange(date) %>% filter(date>=ymd(20040304)) %>% 
  group_by(Fund) %>% 
  mutate(`Net of fees` = coalesce(`Net of fees`, Returns),
         Net.ret = coalesce(`Net of fees`, 0),
         `roi` = cumprod(1 + Net.ret)) %>% 
  ungroup() %>% select(date, Fund, roi)
  

fund_comp %>%
  ggplot(aes(x = date, y = roi, color = Fund)) +
  geom_line() +
  labs(title = "Cumulative Return of Funds Over Time",
       x = "Date",
       y = "Cumulative Return") +
  theme_minimal()
```




