---
title: "q6readme"
author: "Gabriel Rambanapasi"
date: "`r Sys.Date()`"
output: html_document
---

# objetive 

optimize a portfolio given the constraints listed below and tweak depending on own analysis. 



# cnstraints 

- long only 
- When using covariance and mean forecasts, use a look-back of less than 3 years;
- Do not hold any assets with less than 3 years’ returns data;
- Apply Quarterly Rebalancing;
- Limit exposure to Bonds and credit instruments at 25%;
- Limit exposure to Equities at 60%;
- Limit single asset exposure at 40%;

```{r}
# loadings

pacman::p_load(tidyverse)
pacman::p_load(RiskPortfolios);pacman::p_load(fitHeavyTail)
pacman::p_load(quadprog)
StartDate <- lubridate::ymd(20150101)

# Data 

MAA <- read_rds("data/MAA.rds") %>% filter(!Ticker %in% c("DXY Index", 'BCOMTR Index', "ADXY Index")) %>% select(-Name)

# seems like the above could be used to stratify returns 

# read_rds("data/msci.rds") %>% select(Name) %>% distinct()

msci <-
read_rds("data/msci.rds") %>%
filter(Name %in% c("MSCI_ACWI", "MSCI_USA", "MSCI_RE", "MSCI_Jap")) %>%  rename(Ticker = Name)

# One dataframe

combined.data <- bind_rows(MAA, msci) 

# tickers that existed years ago 

comb_assets_3_years <- combined.data %>% group_by(Ticker) %>% filter(date == as.Date("2020/11/25")) %>% pull(Ticker) %>% unique()

# rebalancing quarter days used for filter 

RebMonths <- c("Mar", "Jun", "Oct", "Dec" )


return <- 
  
combined.data %>%
    mutate(M = format(date, "%b"), YM = format(date, "%Y %b")) %>% filter(M %in% RebMonths) %>%filter(Ticker %in% comb_assets_3_years) %>% 
  group_by(Ticker,YM ) %>% 
  filter(date == last(date)) %>%
  ungroup() %>% 
  group_by(Ticker) %>% 
  mutate(ret = log(Price)- lag(log(Price))) %>% slice(-1) %>%  ungroup() %>%select(date, Ticker, ret) %>% 
  spread(Ticker, ret) %>% filter(date > ymd(20101231))


# impute returns for missing dates

return <- impute_missing_returns(return, 'Drawn_Distribution_Collective')

# Using risk portfolos I will determing the mean and covariance matric 

return_mat_Nodate <- data.matrix(return[, -1])

Sigma <- RiskPortfolios::covEstimation(return_mat_Nodate)

Mu <- return %>% summarise(across(-date, ~prod(1+.)^(1/n())-1)) %>% purrr::as_vector()

# to guard against the risk of heavy tails I use the heavy tail package and estimate new mean and covariance matrix

HTT <- fitHeavyTail::fit_mvt(return_mat_Nodate)
mu <- return %>% summarise(across(-date, ~prod(1+.)^(1/n())-1)) %>% purrr::as_vector()
# mu <- HTT$mu
Sigma <- HTT$cov
# Ensure order is the same for mu and Sigma (some optimizers are sensitive to ordering... :( )
mu <- mu[colnames(Sigma)] 
# lastly all covariance matrices need to be positive definite 

Sigma <- as.matrix( Matrix::nearPD(Sigma)$mat)
```
# lets add linear constraints and solve the model

```{r}

# the settings to the optimizer, love quadprog for this 

NStox <- ncol(return_mat_Nodate)
LB = 0.01
UB = 0.4
Eq = 0.6 # max equity exposure
Bonds = 0.25 # max FI exposure
meq = 1


# the hard stuff now, get the matrices 

# AMAT, constraints to be respected when optimizing
# meq are inequality constarints 
# 

Eq_mat <- rbind(matrix(0, nrow = 6, ncol = 4),
                -diag(4))

FI_mat <- rbind(matrix(0, 4, 6), 
                 -diag(6))

Amat <- cbind(1, diag(NStox), -diag(NStox), Eq_mat, FI_mat)

# BVEC for the boc constraints 
bvec <- c(1, rep(LB, NStox), -rep(UB, NStox), -rep(Eq, 4), -rep(Bonds, 6))

  w.opt <-
    quadprog::solve.QP(Dmat = Sigma,
                            dvec = mu,
                            Amat = Amat,
                            bvec = bvec,
                            meq = meq)$solution

 result.QP <- tibble(stocks = colnames(Sigma), weight = w.opt)
 
 # thats a wrap
```


